Standalone Tactics using OpenTheory

### 2012-02-06 paper.tex
fix typo

Besides duplicate initial effort, costs of maintenance can be multiplied over different provers, and improvements in functionality can become restricted to single prover unnecessarily.
For instance, Hurd's first-order prover, Metis~\cite{DBLP:conf/cade/Hurd02}, is integrated in at least three HOL-based provers, but the HOL4 version is very old compared to the latest version in Isabelle/HOL.
Another example is a package for defining recursive functions, TFL~\cite{slindphd}, originally implemented for both Isabelle/HOL and HOL4, but recently superceded in Isabelle/HOL only by Krauss's function definition package~\cite{DBLP:journals/jar/Krauss10}.
The improvements of Krauss's method over TFL ought to be applicable to other HOL-based provers, but a direct re-implementation would require substantial effort.

>>>>

Besides duplicate initial effort, costs of maintenance can be multiplied over different provers, and improvements in functionality can become restricted to a single prover unnecessarily.
For instance, Hurd's first-order prover, Metis~\cite{DBLP:conf/cade/Hurd02}, is integrated in at least three HOL-based provers, but the HOL4 version is very old compared to the latest version in Isabelle/HOL.
Another example is a package for defining recursive functions, TFL~\cite{slindphd}, originally implemented for both Isabelle/HOL and HOL4, but recently superceded in Isabelle/HOL only by Krauss's function definition package~\cite{DBLP:journals/jar/Krauss10}.
The improvements of Krauss's method over TFL ought to be applicable to other HOL-based provers, but a direct re-implementation would require substantial effort.
